BioTime

### 2021-03-10 data-raw/02_biotime_ids.Rmd
Get from pins

### Or, from the grid processing script
```{r}
#file created by 01_biotime_grid.R
load(here::here('data/BioTIME_grid_filtered.Rdata'))
data <- bt_grid_filtered %>%
  rename_with(tolower) %>%
  mutate(species = str_replace(species, "_", " "))

>>>>

### Or, from the grid processing script
```{r}
#file created by 01_biotime_grid.R
#load(here::here('data/BioTIME_grid_filtered.Rdata'))
bt_grid_filtered <- pins::pin_get("bt-grid-filtered", board = "github")

data <- bt_grid_filtered %>%
  rename_with(tolower) %>%
  mutate(species = str_replace(species, "_", " "))
